A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-28 paper.tex
Added a conclusion

>>>>

We presented an extension to an existing bounded synthesis technique that
promotes it to unbounded safety games. The approach taken as whole differs
other synthesis techniques by operating in a counterexample guided abstraction
refinement loop instead of attempting to construct a winning region. The
results show that our approach is useful for solving some classes of games that
have never previously been solved.

Future work includes incorporating the solver into a parallel suite of
communicating solver~\cite{bloem2014}. We also aim experiment with
optimisations by focusing on heuristics for avoiding unhelpful actions as well
as constructing more succinct representations of interpolants.
